Evolution of Processes in Delivering Reliable Software in the European Scientific Arena

### 2018-06-28 paper-ieee-trans.tex
Remove plural on fig 3 caption
Address reviewrs comments 2.4 and 2.5

Major developments carried throughout the years were focused on providing new
functionalities, whereas in the early days the adoption of software engineering methodologies had a lower priority.
The released software was less tested, resulting in a higher rate of
rollbacks and patches applied to production systems, compared to the later projects. Thereby, the stability and
% Comment
%P1 C2 L18: Claiming that stability and reliability was regularly compromised is quite a bold statement -- it needs at least some citations, and preferably some explanation of what forms this compromise took for a few prominent cases.
reliability of the e--Infrastructures was often compromised, affecting
negatively their exploitation by the scientific communities \cite{aiftimiei}.
% Comments
%P1 C2 L24: Was this realisation imposed "from above" e.g. by coordinated EC/ERC oversight, or was it "emergent" from the demands of the independent scientific communities?
It became then apparent the need for a better balance between the addition of new features
and the reliability of the released software. Consequently, incoming projects progressively
devoted a substantial part of the software lifecycle to the improvement of the quality of the
software being delivered. At this point, evolving software engineering practices were considered
and gradually adopted to define and implement quality procedures, the organization of
cross--functional teams and deployment of pilot testbeds.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{images/fig3.png}
\caption{Adoption of Configuration Management tools throughout the project lifetime. Also shown the trend lines
leading to the first release (light cream points and lines), and to the second release (dark blue points and lines).}
\label{fig:fig_confman}
\end{figure}

@@

>>>>

Major developments carried throughout the years were focused on providing new
functionalities, whereas in the early days the adoption of software engineering methodologies had a lower priority 
\cite{datagrid}. The released software was less tested, resulting in a higher rate of
rollbacks and patches applied to production systems, compared to the later projects. Thereby, the stability and
% Comment
%P1 C2 L18: Claiming that stability and reliability was regularly compromised is quite a bold statement -- it needs at least some citations, and preferably some explanation of what forms this compromise took for a few prominent cases.
reliability of the e--Infrastructures was often compromised \cite{lingrand-egee}, leading to outages
in the participant resource centers. Back in the days when Grid middleware was actively developed, researchers 
reported the need of improvements both in terms of reliability and performance \cite{campana-atlas}, eventually 
developing their own custom solutions \cite{kindermann}\cite{mendez-lorenzo} on top of the existing services.

% Comments
%P1 C2 L24: Was this realisation imposed "from above" e.g. by coordinated EC/ERC oversight, or was it "emergent" from the demands of the independent scientific communities?
In an effort to improve the research community's experience, it became apparent the need for a better
balance between the addition of new features and the reliability of the released software. Consequently,
incoming European funding programmes and open calls stressed the fact of devoting a substantial part of the software lifecycle to the improvement of the quality of the
software being delivered. At this point, evolving software engineering practices were considered
and gradually adopted to define and implement quality procedures, the organization of
cross--functional teams and deployment of pilot testbeds.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{images/fig3.png}
\caption{Adoption of Configuration Management tools throughout the project lifetime. Also shown the trend lines
leading to the first release (light cream points and line), and to the second release (dark blue points and line).}
\label{fig:fig_confman}
\end{figure}

@@

\bibitem{lingrand-egee}
D. Lingrand, J. Montagnat, J. Martyniak and D. Colling,
``Analyzing the EGEE production grid workload: application to jobs submission optimization,''
\emph{Workshop on Job Scheduling Strategies for Parallel Processing},
pp. 37--58, May. 2009.

\bibitem{campana-atlas}
S. Campana  \emph{et al.},
``Analysis of the ATLAS Rome production experience on the LHC computing grid,''
\emph{IEEE First International Conference of e-Science and Grid Computing},
pp. 8-pp, 2005.

\bibitem{kindermann}
S. Kindermann, 
``Climate Data Analysis and Grid Infrastructures: Experiences and Perspectives,''
\emph{Grid-Enabling Legacy Applications and Supporting End Users Workshop (GELA)},
vol. 20. 2006.

\bibitem{mendez-lorenzo}
P. Mendez-Lorenzo, J. T. Moscicki and A. Ribon,
``Experiences in the gridification of the Geant4 toolkit in the WLCG/EGEE environment,''
\emph{IEEE Nuclear Science Symposium Conference Record},
vol. 2, 2006.
